Supplement to: Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-17 paper/agujournaltemplate_highlighted.tex
Hopefully last one

\textbf{To compute the depth, we select the EW or the NS component with the larger maximum value of the peak.} We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the \textbf{time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier}. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. \textbf{To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054.} We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of McCrory (2006) along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of Preston (2003). The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor (Qn = 1.3 km) is larger than the depth range of the low-frequency earthquake \textbf{families from ~\citeA{CHE_2017_JGR,CHE_2017_G3} (Qn = 0.9). It is a also larger than the thickness of the flow channel where ~\citeA{SAM_2021} suggest that the LFEs are generated (0.5 to 1.5 km). However}, this may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR,CHE_2017_G3} to locate the low-frequency earthquake families. \\

>>>>

\textbf{To compute the depth, we select the EW or the NS component with the larger maximum value of the peak.} We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the \textbf{time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier}. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. \textbf{To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km.} We did the same analysis for the eight arrays of the experiment \textbf{and each of the tremor-location grid points}. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of ~\citeA{MCC_2006} along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of ~\citeA{PRE_2003}. The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor (Qn = 1.3 km) is larger than the depth range of the low-frequency earthquake \textbf{families from ~\citeA{CHE_2017_JGR,CHE_2017_G3} (Qn = 0.9 km). It is a also larger than the thickness of the flow channel where ~\citeA{SAM_2021} suggest that the LFEs are generated (0.5 to 1.5 km). However}, this may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR,CHE_2017_G3} to locate the low-frequency earthquake families. \\

### 2021-11-17 paper/supplementary_material.tex
Hopefully last one

\documentclass[draft]{agujournal2019}
\usepackage{url}
\usepackage{lineno}
\usepackage[inline]{trackchanges}
\usepackage{soul}
\linenumbers

@@

@@

\newpage

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={5cm 0.5cm 7.5cm 1.5cm},clip]{figures/BH_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Burnt Hill array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 1.5cm},clip]{figures/CL_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Cat Lake array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/DR_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Danz Ranch array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 4cm},clip]{figures/GC_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Gold Creek array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/LC_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Lost Cause array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 0.5cm 4.5cm 1.5cm},clip]{figures/PA_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Port Angeles array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1.5cm},clip]{figures/TB_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Three Bumps array. See caption of Figure 4 for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_timelags.eps}
\caption{Distribution of the time lags between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation for the time windows in cluster 0 (that is the time windows that do not fit well with the stack, left panel) and in cluster 1 (that is the time windows that fit well with the stack, right panel). Top panels are the cross-correlation of the EW component with the vertical component, and bottom panels are the cross-correlation of the NS component with the vertical component. The grey dashed lines correspond to the mean plus or minus the standard deviation. The array and the grid cell are the same as in Figures 1 and 2 of the main text.}
\label{pngfiguresample}
\end{figure}

\bibliography{bibliography}

>>>>

\documentclass[draft]{agujournal2019}
\usepackage{url}
\usepackage{lineno}
\usepackage[inline]{trackchanges}
\usepackage{soul}
\usepackage{longtable}
\usepackage{afterpage}

\linenumbers

@@

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{center}
\begin{longtable}{c c c c c c c}
\caption{Depths, thicknesses and S-to-P time lags}\\
\hline
Latitude grid & Longitude grid & Depth & Thickness & S-to-P time lag & Latitude array & Longitude array \\ 
\hline
\endfirsthead
\hline
Latitude grid & Longitude grid & Depth & Thickness & S-to-P time lag & Latitude array & Longitude array \\ 
\hline
\endhead
\endfoot
\hline
\endlastfoot\
48.00568 & -123.42002 & 31.54815 & 1.65708 & 5.61941 & 48.00568 & -123.08435 \\
48.05060 & -123.42002 & 33.39968 & 4.14569 & 5.83762 & 48.00568 & -123.08435 \\
47.96077 & -123.35288 & 33.60503 & 2.62958 & 5.41716 & 48.00568 & -123.08435 \\
48.00568 & -123.35288 & 35.01803 & 0.50788 & 5.57185 & 48.00568 & -123.08435 \\
48.05060 & -123.35288 & 35.71534 & 0.82604 & 5.64570 & 48.00568 & -123.08435 \\
48.09551 & -123.35288 & 35.39573 & 0.86434 & 5.58676 & 48.00568 & -123.08435 \\
47.87093 & -123.28575 & 34.96605 & 1.92117 & 5.53694 & 48.00568 & -123.08435 \\
47.91585 & -123.28575 & 32.62490 & 2.44170 & 5.21036 & 48.00568 & -123.08435 \\
47.96077 & -123.28575 & 36.59168 & 1.37536 & 5.48916 & 48.00568 & -123.08435 \\
48.00568 & -123.28575 & 35.89275 & 0.91314 & 5.37334 & 48.00568 & -123.08435 \\
48.05060 & -123.28575 & 36.78619 & 0.91691 & 5.50867 & 48.00568 & -123.08435 \\
48.09551 & -123.28575 & 35.53476 & 0.50862 & 5.51101 & 48.00568 & -123.08435 \\
47.87093 & -123.21862 & 31.67542 & 1.92960 & 5.11195 & 48.00568 & -123.08435 \\
47.96077 & -123.21862 & 34.93296 & 1.77697 & 5.09618 & 48.00568 & -123.08435 \\
48.00568 & -123.21862 & 34.22632 & 0.49926 & 4.96042 & 48.00568 & -123.08435 \\
48.05060 & -123.21862 & 36.91445 & 0.91123 & 5.31363 & 48.00568 & -123.08435 \\
48.09551 & -123.21862 & 35.68358 & 1.01354 & 5.31189 & 48.00568 & -123.08435 \\
47.87093 & -123.15149 & 33.98015 & 2.03779 & 5.20434 & 48.00568 & -123.08435 \\
47.91585 & -123.15149 & 36.14101 & 1.37292 & 5.22875 & 48.00568 & -123.08435 \\
47.96077 & -123.15149 & 36.46074 & 1.50402 & 5.10543 & 48.00568 & -123.08435 \\
47.91585 & -123.08435 & 36.49842 & 2.17686 & 5.21478 & 48.00568 & -123.08435 \\
47.96077 & -123.08435 & 35.58549 & 1.80173 & 4.98303 & 48.00568 & -123.08435 \\
47.87093 & -123.01722 & 35.26231 & 2.29227 & 5.34418 & 48.00568 & -123.08435 \\
47.91585 & -123.01722 & 34.62103 & 1.36685 & 5.06163 & 48.00568 & -123.08435 \\
47.96077 & -123.01722 & 35.68984 & 2.22221 & 5.01622 & 48.00568 & -123.08435 \\
47.87093 & -122.95009 & 33.98689 & 2.33013 & 5.35153 & 48.00568 & -123.08435 \\
47.91585 & -122.95009 & 36.14334 & 0.93014 & 5.36226 & 48.00568 & -123.08435 \\
47.96077 & -122.95009 & 38.23725 & 1.87431 & 5.45880 & 48.00568 & -123.08435 \\
47.82602 & -122.81583 & 31.56048 & 2.61761 & 5.86262 & 48.00568 & -123.08435 \\
47.82253 & -123.26401 & 35.74926 & 2.11541 & 5.68370 & 47.95728 & -122.92866 \\
47.86745 & -123.26401 & 41.08041 & 2.87814 & 5.98238 & 47.95728 & -122.92866 \\
47.77762 & -123.19694 & 34.56016 & 3.64623 & 5.52653 & 47.95728 & -122.92866 \\
47.82253 & -123.19694 & 35.43658 & 2.03552 & 5.34851 & 47.95728 & -122.92866 \\
47.86745 & -123.19694 & 39.94581 & 1.62455 & 5.58794 & 47.95728 & -122.92866 \\
47.91236 & -123.19694 & 41.07722 & 1.71031 & 5.59555 & 47.95728 & -122.92866 \\
47.95728 & -123.19694 & 42.49709 & 2.11620 & 5.68647 & 47.95728 & -122.92866 \\
48.00220 & -123.19694 & 39.01816 & 1.71031 & 5.41247 & 47.95728 & -122.92866 \\
48.00220 & -123.12987 & 40.86172 & 2.03982 & 5.33767 & 47.95728 & -122.92866 \\
47.77762 & -123.06280 & 33.16434 & 2.14594 & 4.95932 & 47.95728 & -122.92866 \\
47.82253 & -123.06280 & 34.74994 & 2.03436 & 4.85144 & 47.95728 & -122.92866 \\
47.95728 & -123.06280 & 37.24059 & 1.35377 & 4.74856 & 47.95728 & -122.92866 \\
48.00220 & -123.06280 & 38.05635 & 1.99664 & 4.88688 & 47.95728 & -122.92866 \\
47.91236 & -122.99573 & 38.01949 & 0.44119 & 4.73018 & 47.95728 & -122.92866 \\
47.95728 & -122.99573 & 38.77925 & 1.31783 & 4.79975 & 47.95728 & -122.92866 \\
48.00220 & -122.99573 & 38.64337 & 1.76475 & 4.80089 & 47.95728 & -122.92866 \\
47.95728 & -122.92866 & 38.35029 & 1.30400 & 4.70989 & 47.95728 & -122.92866 \\
48.00220 & -122.92866 & 42.14840 & 1.51672 & 5.15039 & 47.95728 & -122.92866 \\
48.04711 & -122.92866 & 42.26119 & 1.80503 & 5.26400 & 47.95728 & -122.92866 \\
48.05084 & -123.31312 & 36.42203 & 1.44052 & 4.75103 & 48.00593 & -123.31312 \\
48.05084 & -123.24599 & 36.42969 & 0.00000 & 4.77488 & 48.00593 & -123.31312 \\
48.09576 & -123.24599 & 37.39737 & 1.90200 & 5.02892 & 48.00593 & -123.31312 \\
48.18559 & -123.24599 & 47.25344 & 2.15282 & 6.17857 & 48.00593 & -123.31312 \\
48.23051 & -123.24599 & 44.02860 & 1.42896 & 6.19100 & 48.00593 & -123.31312 \\
48.09576 & -123.17885 & 35.08858 & 1.44200 & 4.94872 & 48.00593 & -123.31312 \\
48.14068 & -123.17885 & 47.15230 & 3.02958 & 6.05049 & 48.00593 & -123.31312 \\
48.18559 & -123.17885 & 42.57948 & 2.37736 & 5.95615 & 48.00593 & -123.31312 \\
48.02202 & -122.91146 & 50.93325 & 1.36283 & 6.18599 & 47.93219 & -123.04553 \\
48.06693 & -122.91146 & 49.24794 & 1.91613 & 6.19655 & 47.93219 & -123.04553 \\
48.05494 & -123.53161 & 29.51566 & 0.93316 & 3.50649 & 48.05494 & -123.46442 \\
48.05494 & -123.46442 & 33.80796 & 0.46297 & 4.05934 & 48.05494 & -123.46442 \\
47.97304 & -123.33976 & 35.03636 & 0.00000 & 5.27955 & 47.97304 & -123.13849 \\
47.79337 & -123.27267 & 31.40335 & 1.23311 & 5.23324 & 47.97304 & -123.13849 \\
47.83829 & -123.27267 & 33.70694 & 1.21786 & 5.32252 & 47.97304 & -123.13849 \\
47.88320 & -123.27267 & 35.90145 & 0.92566 & 5.33576 & 47.97304 & -123.13849 \\
47.92812 & -123.27267 & 36.15617 & 0.00000 & 5.23042 & 47.97304 & -123.13849 \\
47.74846 & -123.20558 & 22.82810 & 1.31211 & 5.19491 & 47.97304 & -123.13849 \\
47.79337 & -123.20558 & 34.26325 & 3.64025 & 5.47604 & 47.97304 & -123.13849 \\
47.83829 & -123.20558 & 34.71200 & 1.05090 & 5.28416 & 47.97304 & -123.13849 \\
47.88320 & -123.20558 & 36.22529 & 0.45562 & 5.23800 & 47.97304 & -123.13849 \\
47.92812 & -123.20558 & 38.98809 & 0.00000 & 5.38327 & 47.97304 & -123.13849 \\
47.88320 & -123.13849 & 36.68302 & 0.88185 & 5.23505 & 47.97304 & -123.13849 \\
47.92812 & -123.13849 & 36.54505 & 1.36479 & 5.09592 & 47.97304 & -123.13849 \\
47.92812 & -123.07140 & 39.29662 & 0.41989 & 5.41719 & 47.97304 & -123.13849 \\
47.97304 & -123.07140 & 39.87510 & 0.00000 & 5.46192 & 47.97304 & -123.13849 \\
47.88320 & -123.00431 & 33.30555 & 2.26548 & 5.05178 & 47.97304 & -123.13849 \\
47.92812 & -123.00431 & 38.03179 & 1.36685 & 5.43625 & 47.97304 & -123.13849 \\
47.92812 & -122.93722 & 35.87715 & 2.91725 & 5.41123 & 47.97304 & -123.13849 \\
\hline
\end{longtable}
\end{center}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={5cm 0.5cm 7.5cm 1.5cm},clip]{figures/BH_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Burnt Hill array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 1.5cm},clip]{figures/CL_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Cat Lake array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/DR_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Danz Ranch array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 4cm},clip]{figures/GC_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Gold Creek array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/LC_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Lost Cause array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 0.5cm 4.5cm 1.5cm},clip]{figures/PA_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Port Angeles array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1.5cm},clip]{figures/TB_PWS_PWS_0.eps}
\caption{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Three Bumps array. See caption of Figure 4 from the main text for an explanation of this figure.}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_timelags.eps}
\caption{Time lags between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation are computed for each time window for which the source of the tremor is located on a grid cell. The distribution of the time lags is shown for the time windows in cluster 0 (that is the time windows that do not fit well with the stack, left panel) and in cluster 1 (that is the time windows that fit well with the stack, right panel). Top panels are the cross-correlation of the EW component with the vertical component, and bottom panels are the cross-correlation of the NS component with the vertical component. The grey dashed lines correspond to the mean plus or minus the standard deviation. The array and the grid cell are the same as in Figures 1 and 2 from the main text.}
\label{pngfiguresample}
\end{figure}
